---
title: "Glacier_Project"
author: "The_Leopards"
date: "January 28, 2016"
output: html_document
---



## Glacier Project

The Leopards: Samantha Krawczyk, Georgios Anastasiou

Comparing and visualising change in Landsat images of the Rhone Glacier, Switzerland Glacier extent estimated using NDSI (Normalised Differentiated Snow Index). The method is validated through comparison with GLIMS dataset.

Link to GitHub repository: https://github.com/TheLeopards/Final_Project.git


## Loading functions

```{r sources}
source("R/image_selection.R")
source("R/cloud_water_mask.R")
source("R/calc_NDSI.R")
source("R/plot_with_names.R")
source("R/plot_shp_outlines.R")
```

## checking cloud cover for area of interest; if cloud cover is less than 50% the file is untared. Setting variables for image_selection function

```{r image_selection}
tarList <- list("data/LT51940281984246-SC20160127034926.tar.gz","data/LT51940281990214-SC20160127034923.tar.gz", "data/LT51940282001212-SC20160125050334.tar.gz", "data/LT51940282003218-SC20160127034612.tar.gz", "data/LT51940282003234-SC20160126032814.tar.gz", "data/LT51940282009218-SC20160127034452.tar.gz", "data/LT51940282009250-SC20160127034608.tar.gz","data/LT51940282010221-SC20160125050415.tar.gz", "data/LT51940282010237-SC20160127034442.tar.gz", "data/LT51940282011240-SC20160126032704.tar.gz")
extentArea <- extent(451000, 456500, 5158000, 5167000)
tempFolder <-"data/CloudTemp"
outputFolder <- "output/"
outputNameSubStart <- 6
outputNameSubStop <- 21

image_selection(tarList, extentArea, tempFolder, outputFolder, outputNameSubStart, outputNameSubStop)

```

## Masking the images for water and cloud areas derived from Landsat layer CFmask. Setting variables for cloud_water_mask function

```{r cloud_water_mask}
ImageList <- list.files("output", pattern = "*.grd", full.names = TRUE)
cfmaskLayer <- 5
outputName <- "cloudfree"
outputNameSubStart <- 8
outputNameSubStop <- 24

cloud_water_mask(ImageList, cfmaskLayer, outputFolder, outputName, outputNameSubStart, outputNameSubStop)
```

## Calculating NDSI. Setting variables for calc_NDSI function

```{r calc_NDSI}
ImageList <- list.files("output", pattern = glob2rx("cloud*.grd"), full.names = TRUE)
layerX <- 3
layerY <- 4
outputName <- "NDSI"
outputNameSubStart <- 17
outputNameSubStop <- 33

calc_NDSI(ImageList, layerX, layerY, outputFolder, outputName, outputNameSubStart, outputNameSubStop)
```

## Plotting all glacier areas derived from NDSI. Setting variables for plot_with_names function

```{r plot_with_names}
NDSIlist <- list.files("output", pattern=glob2rx("NDSI*.grd"), full.names=T)
outputNameSubStart <- 14
outputNameSubStop <- 29

plot_with_names(NDSIlist, outputNameSubStart, outputNameSubStop)
```

## plotting glacier outlines on top of each other. Setting variables for plot_shp_outlines function

```{r plot_shp_outlines}
dsn="output"
outputName = "NDSI_shp_"
outputNameSubStart <- 14
outputNameSubStop <- 29
pattern <- glob2rx("NDSI*.shp")
colNum <- 50
main <- "Change in Rhone Glacier"
legendSubStart <-17
legendSubStop <- 32

plot_shp_outlines(NDSIlist, dsn, outputName, outputNameSubStart, outputNameSubStop, pattern, colNum, main, legendSubStart, legendSubStop)
```

## Validating the use of NDSI as a proxy for glacier extent by comparing it with the GLIMS dataset

```{r NDSI_validation}
source("R/NDSI_validation.R")
```



